---
title: "Advance_ML_Contest1"
author: "Ali Alghaithi"
date: "11/8/2020"
output:
  html_document:
    df_print: paged
---

# Reading 
```{r}
# 
#https://uvastatlab.github.io/2019/05/01/getting-started-with-multiple-imputation-in-r/

  
# On the Security of the Automatic Dependent Surveillance-Broadcast Protocol
#https://arxiv.org/pdf/1307.3664.pdf
```

```{r,warning=FALSE}
library(readr)
library(tidyverse)
library(ggmap)

train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
wide <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_wide.csv")
long <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_long.csv")


register_google(key = "AIzaSyBcfF5Tadb-H1Bp7l_XdFFvGS1RjQ94zUs")
has_google_key()
library(ggmap)
library(sf)
library(mapview)




locations_df <- train %>% select(ID, Latitude,Longitude) %>% filter(ID == 1)
locations_df
locations <- as_tibble(locations_df[1:15,])
locations
locations_sf <- st_as_sf(locations, coords = c("Longitude", "Latitude"), crs = 4326)

mapview(locations_sf)


```


```{r,warning=FALSE}
library(readr)
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
wide <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_wide.csv")
long <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_long.csv")
 

summary(train)

library(imputeTS)
for (i in unique(test$ID)){
for (j in 3:7){
test[test$ID == i, j] = na.interpolation(test[test$ID == i, j], option = "stine" )

}
}
test1<- test


test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
for (i in unique(test$ID)){
for (j in 3:7){
test[test$ID == i, j] = na.interpolation(test[test$ID == i, j], option = "linear" )
}
}

test2<- test



test <- (test2+ test1) /2

# test[1:833,3] = F1
# test[1:833,4] = F2
# test[1:833,5] = F3
# test[1:833,6] = F4
 test[1:833,7] = M1[1]




# zoe 
write.csv(test, file="Ali_submission_wide.csv", row.names=FALSE)


##### Change the file path!!! #####
submission = test
submission$IDTime = paste(submission$ID, submission$Time)
## Find the row index of the test set
k = as.vector(by(submission$ID,submission$ID,length))
a = lapply(k, function(x){seq(1,x,by=16)})
m = c(0,cumsum(k)[-80])
b = lapply(1:80,function(i){a[[i]]+m[i]})
i = unlist(b)
## Remove the test set from prediction and generate the long table
dat = submission[-i,-(1:2)]
dat = reshape2::melt(dat,id="IDTime")
dat$ID = paste(dat$IDTime, dat$variable)
## Write the data into a new submission file
write.csv(dat[,4:3], file="Kaggle_submission_long.csv", row.names=FALSE)
```




```{r}
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
wide <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_wide.csv")
long <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_long.csv")
head(test)
test
cor(train)
train1 <- train[2:nrow(train),]
colnames(train1) <- c("newID"  , "newTime"  , "newLatitude" , "newLongitude", "newAltB" ,"newGndSpd" ,"newVSpd" )
all_train<- cbind(train[-nrow(train),],train1)

head(all_train)

cor(all_train)

library(randomForest)


mlm1 <- randomForest(newLatitude ~ Time+Latitude+ Longitude+AltB+GndSpd+VSpd, data = all_train)

mlm1$coefficients

fitted_data<- as.data.frame(mlm1$fitted.values)

tail(fitted_data)
tail(test)



fitted_data[-c(1:69430),]


sub <- test_try
tail(sub)
fitted_data[-c(1:69430),]
sub[,3:4] = fitted_data[-c(1:69430),1:2]
sub

fitted_data[-c(1:69430),1:2]
train
69430 +  208288
277718

fitted_data
 277,717
tail(fitted_data,17)
 tail(test,17)
 plot(mlm1$fitted.values)
library(car)
mlm2 <- update(mlm1, . ~ .)


nd <- as.data.frame(test[i,])
p <- predict(mlm2, nd)


for (i in 1:889) {
if (is.na(test[i+1,3])){i=i}else{i=i+1}
nd <- as.data.frame(test[i,])
p <- predict(mlm2, nd)
test[i+1,3:4] <-as.data.frame(p)
}

new<- test


test[1:889,3:4] = new[1:889,3:4]



##### Change the file path!!! #####
submission = sub
submission$IDTime = paste(submission$ID, submission$Time)
## Find the row index of the test set
k = as.vector(by(submission$ID,submission$ID,length))
a = lapply(k, function(x){seq(1,x,by=16)})
m = c(0,cumsum(k)[-80])
b = lapply(1:80,function(i){a[[i]]+m[i]})
i = unlist(b)
## Remove the test set from prediction and generate the long table
dat = submission[-i,-(1:2)]
dat = reshape2::melt(dat,id="IDTime")
dat$ID = paste(dat$IDTime, dat$variable)
## Write the data into a new submission file
write.csv(dat[,4:3], file="Kaggle_submission_long.csv", row.names=FALSE)
```


4.5 ADS-B GENERAL
Automatic Dependent Surveillance Broadcast
(ADS-B) is a technology where aircraft
avionics broadcasts the aircraft position,
altitude, velocity and other parameters
completely autonomously.
The system is automatic because the pilot is
not involved in initiating broadcasts.
The service is dependent on the aircraft
position determination system.
The application is surveillance, both airground and air-air.
When ADS-B is used, aircraft and other
vehicles continuously broadcast a message
including position, heading, velocity and
intent. Other uses may include obstacles
transmitting a position message. Aircraft,
ground-based stations and other users
monitoring the channels can receive the
information and use it in a wide variety of
applications. Because of this potential for
broad utilization, a system using ADS-B is
most often discussed as a replacement for or
an augmentation to current methods of
monitoring aeronautical traffic.
To understand the full capability of ADS-B,
consider how the current Air Traffic Control
system creates information. The radar
measures the range and bearing of an
aircraft. Bearing is measured by the position
of the rotating radar antenna when it receives
a response to its interrogation from the
aircraft, and range is measured by the time it
takes for the radar to receive the
interrogation response. The antenna beam
becomes wider as the aircraft get farther
away, making the position information less
accurate. Additionally, detecting changes in
aircraft velocity requires several radar
sweeps that are spaced several seconds
apart.
In contrast, a system using ADS-B creates
and listens for periodic position and intent
reports from aircraft. These reports are
generated and distributed using precise
instruments, such as the global positioning
system (GPS) and Mode S transponders,
meaning integrity of the data is no longer
susceptible to the range of the aircraft or the
length of time between radar sweeps. The
enhanced accuracy of the information will be
used to improve safety, support a wide
variety of applications and increase airport
and airspace capacity.
4.5.1 ADS-B/GICB MODES
The IFR 6000 provides flight line test
capability for receiving (ADS-B MON mode),
decoding and displaying full ADS-B
DO-260/A/B DF17/DF18 extended squitter
transmissions from Mode S transponders or
DF18 extended squitters from 1090 MHz
emitters. Capability to generate (ADS-B GEN
mode) full DO-260/A/B DF17/DF18 extended
squitter transmissions for testing ADS-B
receivers is provided. A GICB mode fully
decodes and displays all Enhanced
Surveillance BDS register contents. The
ADS-B/GICB is a Sub-Mode of XPDR Mode




```{r}

library(readr)
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
wide <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_wide.csv")
long <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_long.csv")
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")



library(dplyr)
x <- train %>% filter(ID ==1)

# Latitude
x <- x %>% mutate(startLatitude = NA)
x <- x %>% mutate(EndLatitude = NA)
x <- x %>% mutate(AvgLatitude = NA)
# Longitude
x <- x %>% mutate(startLongitude = NA)
x <- x %>% mutate(EndLongitude = NA)
x <- x %>% mutate(AvgLongitude = NA)

# AltB
x <- x %>% mutate(startAltB = NA)
x <- x %>% mutate(EndAltB = NA)
x <- x %>% mutate(AvgAltB = NA)

# GndSpd
x <- x %>% mutate(startGndSpd = NA)
x <- x %>% mutate(EndGndSpd = NA)
x <- x %>% mutate(AvgGndSpd = NA)

# VSpd
x <- x %>% mutate(startVSpd = NA)
x <- x %>% mutate(EndVSpd = NA)
x <- x %>% mutate(AvgVSpd = NA)

i=1
while(i <= nrow(x)){
  c = i+16
  if(c>nrow(x)){c=nrow(x)}
  # Latitude
 x$startLatitude[i:c] = x$Latitude[i]
 x$EndLatitude[i:c] = x$Latitude[c]
 x$AvgLatitude[i:c] = (x$Latitude[i] + x$Latitude[c])/2
  
#Longitude
 x$startLongitude[i:c] = x$Longitude[i]
 x$EndLongitude[i:c] = x$Longitude[c]
 x$AvgLongitude[i:c] = (x$Longitude[i] + x$Longitude[c])/2

# AltB
 x$startAltB[i:c] = x$AltB[i]
 x$EndAltB[i:c] = x$AltB[c]
 x$AvgAltB[i:c] = (x$AltB[i] + x$AltB[c])/2
# GndSpd
 x$startGndSpd[i:c] = x$GndSpd[i]
 x$EndGndSpd[i:c] = x$GndSpd[c]
 x$AvgGndSpd[i:c] = (x$GndSpd[i] + x$GndSpd[c])/2
 
#VSpd
 x$startVSpd[i:c] = x$VSpd[i]
 x$EndVSpd[i:c] = x$VSpd[c]
 x$AvgVSpd[i:c] = (x$VSpd[i] + x$VSpd[c])/2
 

i= i +16
  }




train1 <- x[2:nrow(x),]
colnames(train1) <- c("step1ID"        ,     "step1Time"       ,    "step1Latitude"  ,     "step1Longitude"  ,   
 "step1AltB"      ,     "step1GndSpd"     ,    "step1VSpd"     ,      "step1startLatitude" ,
 "step1EndLatitude"   , "step1AvgLatitude"   , "step1startLongitude" ,"step1EndLongitude",  
 "step1AvgLongitude",   "step1startAltB"  ,    "step1EndAltB"    ,    "step1AvgAltB"  ,     
 "step1startGndSpd"  ,  "step1EndGndSpd"   ,   "step1AvgGndSpd"  )

train2 <- x[3:nrow(x),]
colnames(train2) <- c("step2ID"        ,     "step2Time"       ,    "step2Latitude"  ,     "step2Longitude"  ,   
 "step2AltB"      ,     "step2GndSpd"     ,    "step2VSpd"     ,      "step2startLatitude" ,
 "step2EndLatitude"   , "step2AvgLatitude"   , "step2startLongitude" ,"step2EndLongitude",  
 "step2AvgLongitude",   "step2startAltB"  ,    "step2EndAltB"    ,    "step2AvgAltB"  ,     
 "step2startGndSpd"  ,  "step2EndGndSpd"   ,   "step2AvgGndSpd"  )


train3 <- x[4:nrow(x),]
colnames(train3) <- c("step3ID"        ,     "step3Time"       ,    "step3Latitude"  ,         "step3Longitude"  ,   
 "step3AltB"      ,     "step3GndSpd"     ,    "step3VSpd"     ,      "step3startLatitude" ,
 "step3EndLatitude"   , "step3AvgLatitude"   , "step3startLongitude" ,"step3EndLongitude",  
 "step3AvgLongitude",   "step3startAltB"  ,    "step3EndAltB"    ,    "step3AvgAltB"  ,     
 "step3startGndSpd"  ,  "step3EndGndSpd"   ,   "step3AvgGndSpd"  )


train4 <- x[5:nrow(x),]
colnames(train4) <- 
  c("step4ID"          ,"step4Time"        ,"step4Latitude"        ,"step4Longitude"     ,   
    "step4AltB"        ,"step4GndSpd"      ,"step4VSpd"            ,"step4startLatitude" ,
    "step4EndLatitude" ,"step4AvgLatitude" ,"step4startLongitude"  ,"step4EndLongitude",  
    "step4AvgLongitude","step4startAltB"   ,"step4EndAltB"         ,"step4AvgAltB"  ,     
    "step4startGndSpd","step4EndGndSpd"   ,"step4AvgGndSpd"  )



train5 <- x[6:nrow(x),]
colnames(train5) <- 
  c("step5ID"          ,"step5Time"        ,"step5Latitude"        ,"step5Longitude"     ,   
    "step5AltB"        ,"step5GndSpd"      ,"step5VSpd"            ,"step5startLatitude" ,
    "step5EndLatitude" ,"step5AvgLatitude" ,"step5startLongitude"  ,"step5EndLongitude",  
    "step5AvgLongitude","step5startAltB"   ,"step5EndAltB"         ,"step5AvgAltB"  ,     
    "step5startGndSpd" ,"step5EndGndSpd"   ,"step5AvgGndSpd"  )



train6 <- x[7:nrow(x),]
colnames(train6) <- 
  c("step6ID"          ,"step6Time"        ,"step6Latitude"        ,"step6Longitude"     ,   
    "step6AltB"        ,"step6GndSpd"      ,"step6VSpd"            ,"step6startLatitude" ,
    "step6EndLatitude" ,"step6AvgLatitude" ,"step6startLongitude"  ,"step6EndLongitude",  
    "step6AvgLongitude","step6startAltB"   ,"step6EndAltB"         ,"step6AvgAltB"  ,     
    "step6startGndSpd" ,"step6EndGndSpd"   ,"step6AvgGndSpd"  )




train7 <- x[8:nrow(x),]
colnames(train7) <- 
  c("step7ID"          ,"step7Time"        ,"step7Latitude"        ,"step7Longitude"     ,   
    "step7AltB"        ,"step7GndSpd"      ,"step7VSpd"            ,"step7startLatitude" ,
    "step7EndLatitude" ,"step7AvgLatitude" ,"step7startLongitude"  ,"step7EndLongitude",  
    "step7AvgLongitude","step7startAltB"   ,"step7EndAltB"         ,"step7AvgAltB"  ,     
    "step7startGndSpd" ,"step7EndGndSpd"   ,"step7AvgGndSpd"  )





train8 <- x[9:nrow(x),]
colnames(train8) <- 
  c("step8ID"          ,"step8Time"        ,"step8Latitude"        ,"step8Longitude"     ,   
    "step8AltB"        ,"step8GndSpd"      ,"step8VSpd"            ,"step8startLatitude" ,
    "step8EndLatitude" ,"step8AvgLatitude" ,"step8startLongitude"  ,"step8EndLongitude",  
    "step8AvgLongitude","step8startAltB"   ,"step8EndAltB"         ,"step8AvgAltB"  ,     
    "step8startGndSpd" ,"step8EndGndSpd"   ,"step8AvgGndSpd"  )


train9 <- x[10:nrow(x),]
colnames(train9) <- 
  c("step9ID"          ,"step9Time"        ,"step9Latitude"        ,"step9Longitude"     ,   
    "step9AltB"        ,"step9GndSpd"      ,"step9VSpd"            ,"step9startLatitude" ,
    "step9EndLatitude" ,"step9AvgLatitude" ,"step9startLongitude"  ,"step9EndLongitude",  
    "step9AvgLongitude","step9startAltB"   ,"step9EndAltB"         ,"step9AvgAltB"  ,     
    "step9startGndSpd" ,"step9EndGndSpd"   ,"step9AvgGndSpd"  )


train10 <- x[11:nrow(x),]
colnames(train10) <- 
  c("step10ID"          ,"step10Time"        ,"step10Latitude"        ,"step10Longitude"     ,   
    "step10AltB"        ,"step10GndSpd"      ,"step10VSpd"            ,"step10startLatitude" ,
    "step10EndLatitude" ,"step10AvgLatitude" ,"step10startLongitude"  ,"step10EndLongitude",  
    "step10AvgLongitude","step10startAltB"   ,"step10EndAltB"         ,"step10AvgAltB"  ,     
    "step10startGndSpd" ,"step10EndGndSpd"   ,"step10AvgGndSpd"  )


train11 <- x[12:nrow(x),]
colnames(train11) <- 
  c("step11ID"          ,"step11Time"        ,"step11Latitude"        ,"step11Longitude"     ,   
    "step11AltB"        ,"step11GndSpd"      ,"step11VSpd"            ,"step11startLatitude" ,
    "step11EndLatitude" ,"step11AvgLatitude" ,"step11startLongitude"  ,"step11EndLongitude",  
    "step11AvgLongitude","step11startAltB"   ,"step11EndAltB"         ,"step11AvgAltB"  ,     
    "step11startGndSpd" ,"step11EndGndSpd"   ,"step11AvgGndSpd"  )

train12 <- x[13:nrow(x),]
colnames(train12) <- 
  c("step12ID"          ,"step12Time"        ,"step12Latitude"        ,"step12Longitude"     ,   
    "step12AltB"        ,"step12GndSpd"      ,"step12VSpd"            ,"step12startLatitude" ,
    "step12EndLatitude" ,"step12AvgLatitude" ,"step12startLongitude"  ,"step12EndLongitude",  
    "step12AvgLongitude","step12startAltB"   ,"step12EndAltB"         ,"step12AvgAltB"  ,     
    "step12startGndSpd" ,"step12EndGndSpd"   ,"step12AvgGndSpd"  )


train13 <- x[14:nrow(x),]
colnames(train13) <- 
  c("step13ID"          ,"step13Time"        ,"step13Latitude"        ,"step13Longitude"     ,   
    "step13AltB"        ,"step13GndSpd"      ,"step13VSpd"            ,"step13startLatitude" ,
    "step13EndLatitude" ,"step13AvgLatitude" ,"step13startLongitude"  ,"step13EndLongitude",  
    "step13AvgLongitude","step13startAltB"   ,"step13EndAltB"         ,"step13AvgAltB"  ,     
    "step13startGndSpd" ,"step13EndGndSpd"   ,"step13AvgGndSpd"  )


train14 <- x[15:nrow(x),]
colnames(train14) <- 
  c("step14ID"          ,"step14Time"        ,"step14Latitude"        ,"step14Longitude"     ,   
    "step14AltB"        ,"step14GndSpd"      ,"step14VSpd"            ,"step14startLatitude" ,
    "step14EndLatitude" ,"step14AvgLatitude" ,"step14startLongitude"  ,"step14EndLongitude",  
    "step14AvgLongitude","step14startAltB"   ,"step14EndAltB"         ,"step14AvgAltB"  ,     
    "step14startGndSpd" ,"step14EndGndSpd"   ,"step14AvgGndSpd"  )


train15 <- x[16:nrow(x),]
colnames(train15) <- 
  c("step15ID"          ,"step15Time"        ,"step15Latitude"        ,"step15Longitude"     ,   
    "step15AltB"        ,"step15GndSpd"      ,"step15VSpd"            ,"step15startLatitude" ,
    "step15EndLatitude" ,"step15AvgLatitude" ,"step15startLongitude"  ,"step15EndLongitude",  
    "step15AvgLongitude","step15startAltB"   ,"step15EndAltB"         ,"step15AvgAltB"  ,     
    "step15startGndSpd" ,"step15EndGndSpd"   ,"step15AvgGndSpd"  )

x <- head(x,-15)
train1<- head(train1,-14)
train2<- head(train2,-13)
train3<- head(train3,-12)
train4<- head(train4,-11)
train5<- head(train5,-10)
train6<- head(train6,-9)
train7<- head(train7,-8)
train8<- head(train8,-7)
train9<- head(train9,-6)
train10<- head(train10,-5)
train11<- head(train11,-4)
train12<- head(train12,-3)
train13<- head(train13,-2)
train14<- head(train14,-1)
train14

```





# Step1_mode_ modeling 
```{r}
Step1_Mdata <- x %>% 
    select(ends_with(c("Latitude","Longitude","AltB","GndSpd","VSpd")))

Step1_Mdata

library(randomForest)
# step1Latitude
mod_step1Latitude<- randomForest(train1$step1Latitude ~.,Step1_Mdata)
# step1Longitude
mod_step1Longitude <- randomForest(train1$step1Longitude ~.,Step1_Mdata)
# step1AltB
mod_step1AltB <- randomForest(train1$step1AltB ~.,Step1_Mdata)
# step1GndSpd
mod_step1GndSpd<- randomForest(train1$step1GndSpd ~.,Step1_Mdata)
# step1VSpd
mod_step1VSpd<-randomForest(train1$step1VSpd ~.,Step1_Mdata)
```


# Step2_mode_ modeling 
```{r}

Step2_Mdata <- cbind(x,train1)
Step2_Mdata <- Step2_Mdata %>% 
    select(ends_with(c("Latitude","Longitude","AltB","GndSpd","VSpd")))

Step2_Mdata
library(randomForest)
# step2Latitude
mod_step2Latitude<- randomForest(train2$step2Latitude ~.,Step2_Mdata)
# step2Longitude
mod_step2Longitude<- randomForest(train2$step2Longitude ~.,Step2_Mdata)
# step2AltB
mod_step2AltB<-randomForest(train2$step2AltB ~.,Step2_Mdata)
# step2GndSpd
mod_step2GndSpd <-randomForest(train2$step2GndSpd ~.,Step2_Mdata)
# step2VSpd
mod_step2VSpd<- randomForest(train2$step2VSpd ~.,Step2_Mdata)
```
# Step3_mode_ modeling 
```{r}

Step3_Mdata <- cbind(x,train1,train2)
Step3_Mdata <- Step3_Mdata %>% 
    select(ends_with(c("Latitude","Longitude","AltB","GndSpd","VSpd")))

library(randomForest)
# step3Latitude
mod_step3Latitude<-randomForest(train3$step3Latitude ~.,Step3_Mdata)
# step3Longitude
mod_step3Longitude<-randomForest(train3$step3Longitude ~.,Step3_Mdata)
# step3AltB
mod_step3AltB<-randomForest(train3$step3AltB ~.,Step3_Mdata)
# step3GndSpd
mod_step3GndSpd<- randomForest(train3$step3GndSpd ~.,Step3_Mdata)
# step3VSpd
mod_step3VSpd <- randomForest(train3$step3VSpd ~.,Step3_Mdata)
```




```{r}
# prepare test data
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")

library(dplyr)
x <- test %>% filter(ID ==31)

# Latitude
x <- x %>% mutate(startLatitude = NA)
x <- x %>% mutate(EndLatitude = NA)
x <- x %>% mutate(AvgLatitude = NA)
# Longitude
x <- x %>% mutate(startLongitude = NA)
x <- x %>% mutate(EndLongitude = NA)
x <- x %>% mutate(AvgLongitude = NA)

# AltB
x <- x %>% mutate(startAltB = NA)
x <- x %>% mutate(EndAltB = NA)
x <- x %>% mutate(AvgAltB = NA)

# GndSpd
x <- x %>% mutate(startGndSpd = NA)
x <- x %>% mutate(EndGndSpd = NA)
x <- x %>% mutate(AvgGndSpd = NA)

# VSpd
x <- x %>% mutate(startVSpd = NA)
x <- x %>% mutate(EndVSpd = NA)
x <- x %>% mutate(AvgVSpd = NA)

i=1
while (i <= 833 ){
  c = i+16
  if(c>833 ){c=833 }
  # Latitude
 x$startLatitude[i:c] = x$Latitude[i]
 x$EndLatitude[i:c] = x$Latitude[c]
x$AvgLatitude[i:c] = (x$Latitude[i] + x$Latitude[c])/2
  
#Longitude
 x$startLongitude[i:c] = x$Longitude[i]
 x$EndLongitude[i:c] = x$Longitude[c]
x$AvgLongitude[i:c] = (x$Longitude[i] + x$Longitude[c])/2

# AltB
 x$startAltB[i:c] = x$AltB[i]
 x$EndAltB[i:c] = x$AltB[c]
x$AvgAltB[i:c] = (x$AltB[i] + x$AltB[c])/2
# GndSpd
 x$startGndSpd[i:c] = x$GndSpd[i]
 x$EndGndSpd[i:c] = x$GndSpd[c]
x$AvgGndSpd[i:c] = (x$GndSpd[i] + x$GndSpd[c])/2

#VSpd
 x$startVSpd[i:c] = x$VSpd[i]
 x$EndVSpd[i:c] = x$VSpd[c]
 x$AvgVSpd[i:c] = (x$VSpd[i] + x$VSpd[c])/2

i= i +16
  }
y<-x



predict(mod_step1Latitude,y[1,])
predict(mod_step1Longitude,y[1,])
predict(mod_step1AltB,y[1,])
predict(mod_step1GndSpd,y[1,])
predict(mod_step1VSpd,y[1,])



```

# Step4_mode_ modeling 
```{r}

Step4_Mdata <- cbind(x,train1,train2,train3)
Step4_Mdata <- Step4_Mdata %>% 
    select(ends_with(c("Latitude","Longitude","AltB","GndSpd","VSpd")))

library(randomForest)
# step1Latitude
randomForest(train4$step4Latitude ~.,Step4_Mdata)
# step1Longitude
randomForest(train4$step4Longitude ~.,Step4_Mdata)
# step1AltB
randomForest(train4$step4AltB ~.,Step4_Mdata)
# step1GndSpd
randomForest(train4$step4GndSpd ~.,Step4_Mdata)
# step1VSpd
randomForest(train4$step4VSpd ~.,Step4_Mdata)
```

# Step5_mode_ modeling 
```{r}
Step5_Mdata <- cbind(x,train1,train2,train3,train4)
Step5_Mdata <- Step5_Mdata %>% 
    select(ends_with(c("Latitude","Longitude","AltB","GndSpd","VSpd")))

library(randomForest)
# step1Latitude
randomForest(train5$step5Latitude ~.,Step5_Mdata)
# step1Longitude
randomForest(train5$step5Longitude ~.,Step5_Mdata)
# step1AltB
randomForest(train5$step5AltB ~.,Step5_Mdata)
# step1GndSpd
randomForest(train5$step5GndSpd ~.,Step5_Mdata)
# step1VSpd
randomForest(train5$step5VSpd ~.,Step5_Mdata)
```


# #################3

```{r}

library(readr)
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
wide <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_wide.csv")
long <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_long.csv")
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")


for (j in unique(train$ID)){

library(dplyr)
x <- train %>% filter(ID ==j)

# Latitude
x <- x %>% mutate(startLatitude = NA)
x <- x %>% mutate(EndLatitude = NA)
x <- x %>% mutate(AvgLatitude = NA)
# Longitude
x <- x %>% mutate(startLongitude = NA)
x <- x %>% mutate(EndLongitude = NA)
x <- x %>% mutate(AvgLongitude = NA)

# AltB
x <- x %>% mutate(startAltB = NA)
x <- x %>% mutate(EndAltB = NA)
x <- x %>% mutate(AvgAltB = NA)

# GndSpd
x <- x %>% mutate(startGndSpd = NA)
x <- x %>% mutate(EndGndSpd = NA)
x <- x %>% mutate(AvgGndSpd = NA)

# VSpd
x <- x %>% mutate(startVSpd = NA)
x <- x %>% mutate(EndVSpd = NA)
x <- x %>% mutate(AvgVSpd = NA)

i=1
while (i <= nrow(x)){
  c = i+16
  if(c>nrow(x)){c=nrow(x)}
  # Latitude
 x$startLatitude[i:c] = x$Latitude[i]
 x$EndLatitude[i:c] = x$Latitude[c]
x$AvgLatitude[i:c] = (x$Latitude[i] + x$Latitude[c])/2
  
#Longitude
 x$startLongitude[i:c] = x$Longitude[i]
 x$EndLongitude[i:c] = x$Longitude[c]
x$AvgLongitude[i:c] = (x$Longitude[i] + x$Longitude[c])/2

# AltB
 x$startAltB[i:c] = x$AltB[i]
 x$EndAltB[i:c] = x$AltB[c]
 x$AvgAltB[i:c] = (x$AltB[i] + x$AltB[c])/2

 # GndSpd
 x$startGndSpd[i:c] = x$GndSpd[i]
 x$EndGndSpd[i:c] = x$GndSpd[c]
 x$AvgGndSpd[i:c] = (x$GndSpd[i] + x$GndSpd[c])/2

#VSpd
 x$startVSpd[i:c] = x$VSpd[i]
 x$EndVSpd[i:c] = x$VSpd[c]
 x$AvgVSpd[i:c] = (x$VSpd[i] + x$VSpd[c])/2


i= i +16
}

if(j==1){x1=x}
x1 <- rbind(x1,x)

}


x1 <- x1[-c(1:1077),]
write.csv(x1, file="train_with_extra_var_and_into.csv", row.names=FALSE)

```














# Ali +Zoe Idea


#Prepare Train
```{r}
library(readr)
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
wide <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_wide.csv")
long <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_long.csv")
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")

library(dplyr)
train = as.data.frame(train)
train1 <- train 
x <- train 

# create test like data
i=2
while (i <= nrow(x)) {
  m= i+14
if(m>nrow(x)){m=nrow(x)}
  x[i:m,3:7] = NA
  i= i +16}

InData1<- x
InData2<- x

library(imputeTS)
for (i in unique(InData1$ID)){
for (j in 3:7){
InData1[InData1$ID == i, j] = na.interpolation(InData1[InData1$ID == i, j], option = "stine" )
}
}


for (i in unique(InData2$ID)){
for (j in 3:7){
InData2[InData2$ID == i, j] = na.interpolation(InData2[InData2$ID == i, j], option = "linear" )
}
}


InData12 <-(InData1+InData2) / 2 


colnames(train1) <- c("yID"  , "yTime"  , "yLatitude" , "yLongitude", "yAltB" ,"yGndSpd" ,"yVSpd" )

all_train<- cbind(InData12,train1)
all_train <- all_train %>% select(ends_with(c("Latitude","Longitude","AltB","GndSpd","VSpd")))

head(all_train)
```


```{r}

library(dplyr)
x <- all_train

# Latitude
x <- x %>% mutate(startLatitude = NA)
x <- x %>% mutate(EndLatitude = NA)
x <- x %>% mutate(AvgLatitude = NA)
# Longitude
x <- x %>% mutate(startLongitude = NA)
x <- x %>% mutate(EndLongitude = NA)
x <- x %>% mutate(AvgLongitude = NA)

# AltB
x <- x %>% mutate(startAltB = NA)
x <- x %>% mutate(EndAltB = NA)
x <- x %>% mutate(AvgAltB = NA)

# GndSpd
x <- x %>% mutate(startGndSpd = NA)
x <- x %>% mutate(EndGndSpd = NA)
x <- x %>% mutate(AvgGndSpd = NA)

# VSpd
x <- x %>% mutate(startVSpd = NA)
x <- x %>% mutate(EndVSpd = NA)
x <- x %>% mutate(AvgVSpd = NA)

i=1
while (i <= nrow(x)){
  c = i+16
  if(c>nrow(x)){c=nrow(x)}
  # Latitude
 x$startLatitude[i:c] = x$Latitude[i]
 x$EndLatitude[i:c] = x$Latitude[c]
x$AvgLatitude[i:c] = (x$Latitude[i] + x$Latitude[c])/2
  
#Longitude
 x$startLongitude[i:c] = x$Longitude[i]
 x$EndLongitude[i:c] = x$Longitude[c]
x$AvgLongitude[i:c] = (x$Longitude[i] + x$Longitude[c])/2

# AltB
 x$startAltB[i:c] = x$AltB[i]
 x$EndAltB[i:c] = x$AltB[c]
 x$AvgAltB[i:c] = (x$AltB[i] + x$AltB[c])/2

 # GndSpd
 x$startGndSpd[i:c] = x$GndSpd[i]
 x$EndGndSpd[i:c] = x$GndSpd[c]
 x$AvgGndSpd[i:c] = (x$GndSpd[i] + x$GndSpd[c])/2

#VSpd
 x$startVSpd[i:c] = x$VSpd[i]
 x$EndVSpd[i:c] = x$VSpd[c]
 x$AvgVSpd[i:c] = (x$VSpd[i] + x$VSpd[c])/2


i= i +16
  }

#write.csv(test, file="Ali_submission_wide.csv", row.names=FALSE)



```





# model part 
```{r}
mLatitude <- lm(yLatitude ~  Latitude*Longitude*VSpd*GndSpd*AltB, data = all_train)
mLongitude <- lm( yLongitude~ Latitude*Longitude*VSpd*GndSpd*AltB, data = all_train)
mAltB<- lm( yAltB~ Latitude*Longitude*VSpd*GndSpd*AltB, data = all_train)
mGndSpd <- lm( yGndSpd~ Latitude*Longitude*VSpd*GndSpd*AltB, data = all_train)
mVSpd <- lm( yVSpd~ Latitude*Longitude*VSpd*GndSpd*AltB ,data = all_train)

```



# predictions part 
```{r}
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")

test1 <- test %>% filter(ID ==33)
library(dplyr)
x <- test %>% filter(ID ==33)

InData1<- x
InData2<- x

library(imputeTS)
for (i in unique(InData1$ID)){
for (j in 3:7){
InData1[InData1$ID == i, j] = na.interpolation(InData1[InData1$ID == i, j], option = "stine" )
}
}


for (i in unique(InData2$ID)){
for (j in 3:7){
InData2[InData2$ID == i, j] = na.interpolation(InData2[InData2$ID == i, j], option = "linear" )
}
}

InData12 <-(InData1+InData2) / 2 


library(dplyr)
x <- InData12

# Latitude
x <- x %>% mutate(startLatitude = NA)
x <- x %>% mutate(EndLatitude = NA)
x <- x %>% mutate(AvgLatitude = NA)
# Longitude
x <- x %>% mutate(startLongitude = NA)
x <- x %>% mutate(EndLongitude = NA)
x <- x %>% mutate(AvgLongitude = NA)

# AltB
x <- x %>% mutate(startAltB = NA)
x <- x %>% mutate(EndAltB = NA)
x <- x %>% mutate(AvgAltB = NA)

# GndSpd
x <- x %>% mutate(startGndSpd = NA)
x <- x %>% mutate(EndGndSpd = NA)
x <- x %>% mutate(AvgGndSpd = NA)

# VSpd
x <- x %>% mutate(startVSpd = NA)
x <- x %>% mutate(EndVSpd = NA)
x <- x %>% mutate(AvgVSpd = NA)

i=1
while (i <= nrow(x)){
  c = i+16
  if(c>nrow(x)){c=nrow(x)}
  # Latitude
 x$startLatitude[i:c] = x$Latitude[i]
 x$EndLatitude[i:c] = x$Latitude[c]
x$AvgLatitude[i:c] = (x$Latitude[i] + x$Latitude[c])/2
  
#Longitude
 x$startLongitude[i:c] = x$Longitude[i]
 x$EndLongitude[i:c] = x$Longitude[c]
x$AvgLongitude[i:c] = (x$Longitude[i] + x$Longitude[c])/2

# AltB
 x$startAltB[i:c] = x$AltB[i]
 x$EndAltB[i:c] = x$AltB[c]
 x$AvgAltB[i:c] = (x$AltB[i] + x$AltB[c])/2

 # GndSpd
 x$startGndSpd[i:c] = x$GndSpd[i]
 x$EndGndSpd[i:c] = x$GndSpd[c]
 x$AvgGndSpd[i:c] = (x$GndSpd[i] + x$GndSpd[c])/2

#VSpd
 x$startVSpd[i:c] = x$VSpd[i]
 x$EndVSpd[i:c] = x$VSpd[c]
 x$AvgVSpd[i:c] = (x$VSpd[i] + x$VSpd[c])/2


i= i +16
  }



```












# Prediction part 
```{r}
F1 <- predict(mLatitude,InData12)
F2 <- predict(mLongitude,InData12)
F3 <- predict(mAltB,InData12)  
F4 <- predict(mGndSpd,InData12)
F5 <- predict(mVSpd,InData12)


M1 <- predict(mLatitude,InData12)
M2 <- predict(mLongitude,InData12)
M3 <- predict(mAltB,InData12)  
M4 <- predict(mGndSpd,InData12)
M5 <- predict(mVSpd,InData12)

```



```{r}
install.packages("mi")
library(mi)

mi_test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
mi_test$Latitude<- as.data.frame.vector(mi_test$Latitude)
mi_test$Longitude<- as.vector(mi_test$Longitude)


mi_data <- mi(mi_test[3:4], seed = 335)
```



# Fitting method
```{r}
library(data.table)
library(forecast)
library(plyr)
library(readr)
library(imputeTS)
library(dplyr)

train <- read_csv("~/Box/Advance NL Class/Contest1/train_with_extra_var_and_into.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test_with_extra_var_and_into.csv")
InData12 <- test

output <- matrix(ncol=30, nrow=833)

for (i in unique(train$ID)){
new_train <- train %>% filter(ID==i)

ts_fit = function(new_train) {
  VSpd <- ts(new_train$VSpd,frequency = 16)
  EndLatitude <- new_train$EndLatitude
  startLatitude <- new_train$startLatitude
  EndLongitude <- new_train$EndLongitude
  startLongitude <- new_train$startLongitude
  startAltB <- new_train$startAltB
  EndAltB <- new_train$EndAltB
  AvgLatitude <- new_train$AvgLatitude
  
  EndVSpd <- new_train$EndVSpd
  startVSpd <- new_train$startVSpd
  EndGndSpd <- new_train$EndGndSpd
  startGndSpd <- new_train$startGndSpd
  AvgVSpd <- new_train$AvgVSpd
  AvgGndSpd <- new_train$AvgGndSpd
  
  fit <- tslm(VSpd ~ trend  + season    + EndVSpd+ startVSpd +EndGndSpd+startGndSpd+EndLatitude+startLatitude +startLongitude+ EndLongitude+startAltB+EndAltB+AvgVSpd+AvgGndSpd )
  return(fit)
}

model_fit<- ts_fit(new_train)
forecast <- forecast(model_fit, newdata = InData12)
  
M1<- as.data.frame(forecast$mean)
output[,i] <- M1$x

}

as.data.frame(output)


#V14as.data.frame(rowSums(as.data.frame(output))/30)

test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
while (i <= 833){
  
  if(test$VSpd[1:833]== "NA"){test$VSpd[i]=V14[i]}
}
```

```{r,warning=FALSE}
library(readr)
train <- read_csv("~/Box/Advance NL Class/Contest1/train.csv")
test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
wide <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_wide.csv")
long <- read_csv("~/Box/Advance NL Class/Contest1/sample_submission_long.csv")
 

summary(train)

library(imputeTS)
for (i in unique(test$ID)){
for (j in 3:7){
test[test$ID == i, j] = na.interpolation(test[test$ID == i, j], option = "stine" )

}
}
test1<- test


test <- read_csv("~/Box/Advance NL Class/Contest1/test.csv")
for (i in unique(test$ID)){
for (j in 3:7){
test[test$ID == i, j] = na.interpolation(test[test$ID == i, j], option = "linear" )
}
}

test2<- test

test <- (test2+ test1) /2


as.data.frame(M1)
test[5011:8484,3] = M1
test[5011:8484,4] = M2
test[5011:8484,5] = M3
test[5011:8484,6] = M4
test[5011:8484,7] = M5

test[834:5010,3] = F1
test[834:5010,4] = F2
test[834:5010,5] = F3
test[834:5010,6] = F4
test[834:5010,7] = F5

#test[1:833,7] = F7$`rowSums(as.data.frame(output))/30`



# zoe 
write.csv(test, file="Ali_submission_wide.csv", row.names=FALSE)


##### Change the file path!!! #####
submission = test
submission$IDTime = paste(submission$ID, submission$Time)
## Find the row index of the test set
k = as.vector(by(submission$ID,submission$ID,length))
a = lapply(k, function(x){seq(1,x,by=16)})
m = c(0,cumsum(k)[-80])
b = lapply(1:80,function(i){a[[i]]+m[i]})
i = unlist(b)
## Remove the test set from prediction and generate the long table
dat = submission[-i,-(1:2)]
dat = reshape2::melt(dat,id="IDTime")
dat$ID = paste(dat$IDTime, dat$variable)
## Write the data into a new submission file
write.csv(dat[,4:3], file="Kaggle_submission_long.csv", row.names=FALSE)
```

